Fig2: Candidate genes

### 2020-04-17 analysis/figure-2.Rmd
wide figure

makelineplots <- function(whichtissue, whichgenes){

  p <- candidatevsd %>%
    filter(tissue == whichtissue,
          gene %in% whichgenes) %>%
    mutate(treatment = factor(treatment, levels = charlevels)) %>%
    mutate(treatmentNum = as.numeric(treatment)) %>%
    ggplot(aes(x = treatmentNum, y = counts)) +
    geom_boxplot(aes(fill = treatment, color = sex), outlier.shape = NA) +
    #geom_smooth(aes(color = sex)) +
    geom_jitter(size = 0.5, aes(color = sex)) +
    facet_grid(gene~sex, scales = "free") +
    scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9),
                       labels = charlevels) +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme_B3() + 
    theme(legend.position = "none",
          strip.text.y = element_text(face = "italic"),
          axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(subtitle = whichtissue, 
         y = "gene expression (variance stabilized)",
         x = "Parental Care Stage") 
  return(p)
}

a <- makelineplots("hypothalamus", hypDEGs)
b <- makelineplots("pituitary", pitDEGs) + labs(y = NULL)
c <- makelineplots("gonad", gonadDEGs) + labs(y = NULL)

plot_grid(a,b,c, nrow = 1, labels = "AUTO", label_size = 8)
```

>>>>

candidateboxplot <- function(whichtissue, whichgenes, whichsex){

  p <- candidatevsd %>%
    filter(tissue %in% whichtissue,
          gene %in% whichgenes,
          sex %in% whichsex) %>%
    mutate(treatment = factor(treatment, levels = charlevels)) %>%
    mutate(treatmentNum = as.numeric(treatment)) %>%
    ggplot(aes(x = treatmentNum, y = counts)) +
    geom_boxplot(aes(fill = treatment, color = sex), outlier.shape = NA) +
    #geom_smooth(aes(color = sex)) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    facet_wrap(~gene, scales = "free_y", nrow = 1) +
    scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9),
                       labels = charlevels) +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme_B3() + 
    theme(legend.position = "none",
          strip.text = element_text(face = "italic"),
          axis.text.x = element_blank()) +
    labs(subtitle = whichsex,
         y = "gene expression",
         x = NULL) 
  return(p)
}

a1 <- candidateboxplot("hypothalamus", hypDEGs, "female") + labs(x = NULL, title = "hypothalamus") 
a2 <- candidateboxplot("hypothalamus", hypDEGs, "male") + labs(x = NULL) +
  theme(strip.text = element_blank())

b1 <- candidateboxplot("pituitary", pitDEGs, "female") + labs(x = NULL, title = "pituitary")
b2 <- candidateboxplot("pituitary", pitDEGs, "male") + labs(x = NULL) +
  theme(strip.text = element_blank())

c1 <- candidateboxplot("gonad", gonadDEGs, "female") + labs(x = NULL, title = "gonad")
c2 <- candidateboxplot("gonad", gonadDEGs, "male") + 
  theme(strip.text = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1))

plot_grid(a1,a2, b1,b2, c1,c2, nrow = 6, labels = c("A", " ","B", " ", "C", " "), label_size = 8,
          rel_heights = c(1, 0.75, 1, 0.75, 1, 1))
```
